Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-03-17 sas2015/content/impl.tex
cases -> case

To evaluate the practicality of our work, we applied two variants of the IFDS taint analysis
to the SPEC JVM98 benchmarks: (i) an equivalent IDE taint analysis obtained using $\transEq$, and (ii)
an IDE taint analysis obtained using   $\transCC_\rcc$ that avoids imprecision due to correlated method
calls. Unfortunately, for the specific combination of this IFDS client analysis and these benchmark
programs, the precise tracking of data flow in the presence of correlated calls does not impact precision. 
However, the good news is that the running times of the two analyses are roughly the same, ranging from 
a few seconds on the smaller SPEC programs to about two hours on \texttt{javac} in each cases (see the Appendix
for more details on these results).  This suggests that the overhead of tracking correlated calls is manageable,
and that our technique may be worthwhile in other scenarios.

>>>>

To evaluate the practicality of our work, we applied two variants of the IFDS taint analysis
to the SPEC JVM98 benchmarks: (i) an equivalent IDE taint analysis obtained using $\transEq$, and (ii)
an IDE taint analysis obtained using   $\transCC_\rcc$ that avoids imprecision due to correlated method
calls. Unfortunately, for the specific combination of this IFDS client analysis and these benchmark
programs, the precise tracking of data flow in the presence of correlated calls does not impact precision. 
However, the good news is that the running times of the two analyses are roughly the same, ranging from 
a few seconds on the smaller SPEC programs to about two hours on \texttt{javac} in each case (see the Appendix
for more details on these results).  This suggests that the overhead of tracking correlated calls is manageable,
and that our technique may be worthwhile in other scenarios.
